tabla_mean_values Mhuber

### 2017-09-15 analysis/tables_resiliences.Rmd
create tables

### Tablas 
```{r}
evi_a <- mhuber_eviA %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  unite("value", c("value", "Letter"), sep= "^") %>% 
  dplyr::select(var, disturb_year, value) %>% as.data.frame()

evi_a %>% pander() 
```

>>>>

### Tablas Disturb year  
```{r}
evi_a <- mhuber_eviA %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, disturb_year, value_EVI, letter_EVI=Letter) %>% as.data.frame()

evi_a %>% pander()

bai_a <- mhuber_baiA %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_BAI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, disturb_year, value_BAI, letter_BAI=Letter) %>% as.data.frame()

bai_a %>% pander()

mhuberA <- evi_a %>% inner_join(bai_a, by=c("var", "disturb_year"))

mhuberA %>% pander()

mhuberA

```

# Tablas site
```{r}
evi_b <- mhuber_eviB %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, site, value_EVI, letter_EVI=Letter) %>% as.data.frame()

evi_b %>% pander()

bai_b <- mhuber_baiB %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_BAI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, site, value_BAI, letter_BAI=Letter) %>% as.data.frame()

bai_b %>% pander()

```

# Tablas Interaction
```{r}
evi <- mhuber_evi %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var,  disturb_year, site, value_EVI, letter_EVI=Letter) %>% as.data.frame()

evi %>% pander()

bai <- mhuber_bai %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_BAI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, disturb_year, site, value_BAI, letter_BAI=Letter) %>% as.data.frame()

bai %>% pander() 
```
